Adaption of the Chumbley Score to matching of bullet striation marks

### 2017-10-01 doc/paper.Rmd
fiddling

Figure \ref{fig:type1} compares nominal (fixed) type I error and actually observed type I errors for the parameter settings in table XXX.

@@

```{r}
ns <- all %>% group_by(wv, wo, match) %>% summarize(
  n_ss = mean(same_shift_n),
  n_ds = mean(diff_shift_n),
  miss = sum(is.na(p_value))
)
ns %>% filter(wv %in% c(30, 50)) %>% 
  ggplot(aes(x = match, y = n_ds, shape=match, colour = factor(wv))) + 
  geom_point() + geom_line(aes(group=wv)) + facet_wrap(~wo)
```

>>>>

Figure \ref{fig:type1} compares nominal (fixed) type I error and actually observed type I errors for the parameter settings in table XXX. With an increasing size of the window used in the optimization step the observed type I error rate decreases (slighty). This might be related to the increasing number of tests that fail for larger window sizes, in particular for non-matching striae (see fig \ref{fig:missings}).

@@

```{r missings, fig.width=8, fig.height=5, fig.cap="Number of failed tests."}
ns <- all %>% group_by(wv, wo, match) %>% summarize(
  n_ss = mean(same_shift_n),
  n_ds = mean(diff_shift_n),
  zero_ss = sum(same_shift_n==0),
  zero_ds = sum(diff_shift_n==0),
  miss = sum(is.na(p_value))
)
ns %>% filter(wv %in% c(30, 50)) %>% 
  ggplot(aes(x = wo, y = miss/85491*100, shape=factor(wv), colour = factor(match))) + 
  geom_point() + 
  theme_bw() +
  ylab("Percent of failed tests.")
```
